Pesticides pollution of small streams in Germany

### 2016-07-27 article.tex
added lc50 to supplement

\subsection{Characterization of chemical pollution}
We characterized chemical pollution using three indicators:

\begin{enumerate}
  \item National and international Environmental Quality Standards (EQS) \citep{ogewv_verordnung_2011,european_union_directive_2013}:
  We used only Maximum Annual Concentration EQS (MAC-EQS) for characterization.
  \item Regulatory Acceptable Concentrations (RAC) \citep{brock_linking_2010}:
  This is the lowest concentration at which no acceptable biological effects are expected. 
  These are derived during authorization  process of pesticides and contain an uncertainty factor.
  The German Federal Environmental Agency provided RACs for this study.  
  We expressed  RAC as Risk Quotient (RQ)

  \begin{equation}
  RQ = \frac{C}{RAC}
  \end{equation}

  Where $C$ is the concentration of a compound in a sample.

@@

We used Multidimensional Scaling (MDS) based on jaccard dissimilarity in conjunction with hierarchical clustering to display differences in the spectra of analysed compounds per federal state.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{fig/figvar.pdf}
  \caption{Compound spectra of the different federal states. Left: Barcode plot - Each vertical line is an analysed compound. Right: MDS ordination. 
  Colors according to three groups determined by hierarchical clustering (see Supplement Figure (xxx).}
  \label{fig:figvar}
\end{figure}

The distribution of sampling sites across catchment area and agricultural area in the catchment revealed a sharp decline in the distribution of catchment-sizes below $10~km^2$, with most sampling sites with catchments between 10 and 25 $km^2$ (Figure \ref{fig:figezglu}).
The proportion of agriculture in the catchments decreased with increasing catchment size.

@@

@@

\subsection{Subsection}

>>>>

\subsection{Characterization of chemical pollution}
We characterized chemical pollution (excluding sum parameters) using three indicators:

\begin{enumerate}
  \item National and international Environmental Quality Standards (EQS) \citep{ogewv_verordnung_2011,european_union_directive_2013}:
  We used only Maximum Annual Concentration EQS (MAC-EQS) for characterization.
  These were available for 29 compounds (Supplement, Table xxx\todo{ref}).

  \item Regulatory Acceptable Concentrations (RAC) \citep{brock_linking_2010}:
  This is the lowest concentration at which no acceptable biological effects are expected. 
  These are derived during authorization  process of pesticides and contain an uncertainty factor.
  The German Federal Environmental Agency provided RACs for 105 compounds (Supplement, Table xxx\todo{ref}).  
  We expressed RAC as Risk Quotient (RQ):
  \begin{equation}
  RQ = \frac{C}{RAC}
  \end{equation}
  Where $C$ is the concentration of a compound in a sample.

@@

All data-processing and analyses have been performed using R, version 3.3.1 \citep{r_core_team_r:_2016}.
To display differences in the spectra of analysed compounds between federal states we used Multidimensional Scaling (MDS) based on Jaccard dissimilarity in conjunction with hierarchical clustering using the vegan package \citep{oksanen_vegan:_2016}.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{fig/figvar.pdf}
  \caption{Compound spectra of the different federal states. Left: Barcode plot - Each vertical line is an analysed compound. Right: MDS ordination. 
  Colors according to three groups determined by hierarchical clustering (see Supplement Figure (xxx).}
  \label{fig:figvar}
\end{figure}
\todo{prettify figure!}

We were able to derive for 2376 sites catchment sizes and the proportion of agriculture within catchments. \todo{Check why there are so many missing in BW, NW, RP, SN and TH = phchsitesinfo}.
The distribution of sampling sites across catchment area and agricultural area in the catchment revealed a sharp decline in the distribution of catchment-sizes below $10~km^2$, with most sampling sites with catchments between 10 and 25 $km^2$ (Figure \ref{fig:figezglu}).
The proportion of agriculture in the catchments decreased with increasing catchment size.

@@

\todo{1-2 worte das es nicht überall möglich war ezg größe zu bestimmen.}

@@

\subsection{Representativeness of the data}

\subsection{Influence of catchment area and agriculture}

\subsection{Pollution of streams}
